---
title: "rbtl-fs24 end-of-semester exam"
subtitle: "Section 03"
format:
  html:
    embed-resources: true
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **13 out of 53**. The number of points for each task is shown in parenthesis next to the task number.

# Task 3.1 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

You will work with the `generation` and the the `treatment_long` data objects.

```{r}
generation <- read_csv("data/what-a-waste/waste-generation.csv")
treatment_long <- read_csv("data/what-a-waste/treatment-long.csv")
```

# Task 3.1 (1)

1.  Use a function of the family of \*\_join functions to join the `treatment_long` data object with the `generation` data object.

2.  Save the result as a new data object called `treatment_generation`.

```{r}

```

# Task 3.2 (11)

This task requires you to write a code sequence with several steps. It is up to you if you create intermediate data objects and how you name the variables. Use functions you have learned in the course to answer the following three questions.

1.  How many tons of waste per year are openly dumped per in Sri Lanka and Bhutan?

2.  How many kgs per person per day are openly dumped in Sri Lanka and Bhutan?

3.  How much of the total waste generated by all cities is openly dumped (in tons per year and percent).

```{r}


```

# Task 3.6 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
