---
title: "rbtl-fs24 end-of-semester exam"
subtitle: "Section 01"
format:
  html:
    embed-resources: true
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **12 out of 53**. The number of points for each task is shown in parenthesis next to the task number.

# Task 2.0 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

```{r}
generation <- read_csv("data/what-a-waste/waste-generation.csv")
dictionary <- read_csv("data/what-a-waste/dictionary.csv")
```

# Task 2.1 (1)

1.  Explore the dictionary data object to learn more about the data.

```{r}

```

# Task 2.2 (1)

1.  Use the `filter()` function to remove all NAs from the `generation` data object.

2.  Store the result as a new object in your environment with the name `generation_complete`.

```{r}

```

# Task 2.3 (2)

1.  Use the `mutate()` function to add a new column to `generation_complete` that is the municipal solid waste generation per person in kg/day. Name the column `waste_generation_person_kg_day`.

2.  Use the pipe operator to add another line of code which uses the `relocate()` function to move the `waste_generation_person_kg_day` after the `city` column.

3.  Use the pipe operator to add another line of code which uses the `select()` function to remove the `waste_generation` column.

4.  Store the result as a new object in your environment with the name `generation_person`.

```{r}

```

# Task 2.4 (2)

1.  Starting with `generation_person`, use a function of the slice family of functions to return the 5 countries with the highest municipal solid waste generation.

2.  Use the pipe operator to add another line of code, then use a function you have learnt in the course to display a formatted version of the returned dataframe from the previous step.

```{r}

```

# Task 2.5 (5)

1.  Use the data stored in `generation_person` to prepare a box- and jitterplot that displays income on the x-axis and municipal solid waste generation per person on the y-axis.

2.  Add a color aesthetic for the income categories.

3.  Set the width of the jitter to a value of 0.2.

4.  Set the transparency for the points in the jitter to a value of 0.75.

5.  Set the size of the points in the jitter to a value of 2.

6.  Do not display the outliers for the boxplot.

7.  Change the color palette to colors of your choice.

8.  Remove the legend from the plot.

```{r}


```

# Task 2.6 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
