---
title: "rbtl-fs24 end-of-semester exam"
subtitle: "Section 02"
format:
  html:
    embed-resources: true
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **9 out of 53**. The number of points for each task is shown in parenthesis next to the task number.

# Task 3.0 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

```{r}
treatment <- read_csv("data/what-a-waste/waste-treatment.csv")
```

# Task 3.1 (0.5)

1.  Explore the treatment data object using functions taught during the course.

```{r}

```

# Task 3.2 (2)

The `treatment` data does not follow tidy data principles. It is in a wide format rather than in a long format and shows different types of waste treatment in different columns, which could be one column with the type of treatment and another column with the value of the treatment.

1.  Use functions taught in the course to create a new object called `treatment_long` that follows tidy data principles.

2.  Remove NAs from the data.

3.  Store the result as a new object in your environment with the name `treatment_long`.

```{r}

```

# Task 3.1 (1)

1.  Starting with the `treatment_long` data object, use functions taught during the course to answer the following question:

How many cities are covered in this dataset?

```{r}

```

# Task 3.2 (3)

1.  Starting with the `treatment_long` data object, use functions taught during the course to answer the following question:

Which country has the greatest number of cities in the dataset, and how many cities is that?

```{r}


```

# Task 3.3 (1.5)

1.  Starting with the `treatment_long` data object, use functions taught during the course to answer the following question:

In how many cities is all waste (100%) openly dumped?

```{r}

```

# Task 3.4 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
